draft

### 2020-02-27 src/draft.Rmd
Update draft.Rmd
EDA plots updated

2. plots
```{r}

@@

>>>>

2. pct_plots
plot pct change of mill rates
```{r}
dat_1<-data_final %>% subset(Municipalities == "Vancouver") %>% subset(TaxClassCode == "01")
dat_1
dat_1$rate_pct
plot(dat_1$rate_pct)

municipality.list = c(
  "Burnaby", 
  "Coquitlam", 
  "Delta", 
  "Langley - City", 
  "Langley - Township",
  "Maple Ridge",
  "Maple Ridge Rural", 
  "North Vancouver - City",
  "North Vancouver - Dist",
  "Pitt Meadows", 
  "Port Coquitlam", 
  "Port Moody", 
  "Richmond", 
  "Surrey", 
  "Vancouver", 
  "White Rock", 
  "West Vancouver", 
  "Bowen Island", 
  "Anmore", 
  "Belcarra",
  "Lions Bay")
tax.list<-c("01","05","06")
tax.list[1]
# overtall trend for tax class 1
for (i in 1:3){
  plot<-data_final %>% 
  filter(Municipalities %in% municipality.list) %>%
  filter(TaxClassCode == tax.list[i]) %>%
  ggplot(aes(x=Year, y=rate_pct, group=Municipalities, color=Municipalities)) +
    geom_line();
  print(plot)
}

# for each municipality

for (i in 1:21){
  plot<-data_final %>% filter(Municipalities == municipality.list[i]) %>% 
  filter(TaxClassCode %in% tax.list) %>% 
  ggplot(aes(x=Year, y=rate_pct, group=TaxClassCode, color=TaxClassCode)) +
    geom_line()
  print(plot)
}

@@

plot pct change of assessment
```{r}
# total trend of assessment 
for (i in 1:21){
  plot<-data_final %>% filter(Municipalities == municipality.list[i]) %>% 
  filter(TaxClassCode %in% tax.list) %>% 
  ggplot(aes(x=Year, y=assessTotal_pct, group=TaxClassCode, color=TaxClassCode)) +
    geom_line()
  print(plot)
}
```

plot pct change of tax(budget)
```{r}
# total trend for budget 
for (i in 1:21){
  plot<-data_final %>% filter(Municipalities == municipality.list[i]) %>% 
  filter(TaxClassCode %in% tax.list) %>% 
  ggplot(aes(x=Year, y=tax, group=TaxClassCode, color=TaxClassCode)) +
    geom_line()
  print(plot)
}
```

```{r}
# plot rate and assessment for each municipality.

for (i in 1:21){
  test1<-data_final %>% filter(Municipalities == municipality.list[i]) %>% 
  filter(TaxClassCode %in% tax.list) %>% 
  ggplot(aes(x=Year, y=rate_pct, group=TaxClassCode, color=TaxClassCode)) +
   geom_line()

  test2<-data_final %>% filter(Municipalities == municipality.list[i]) %>% 
  filter(TaxClassCode %in% tax.list) %>% 
  ggplot(aes(x=Year, y=assessTotal_pct, group=TaxClassCode, color=TaxClassCode)) +
   geom_line()

  test3<-data_final %>% filter(Municipalities == municipality.list[i]) %>% 
  filter(TaxClassCode %in% tax.list) %>% 
  ggplot(aes(x=Year, y=assessTotal_pct, group=TaxClassCode, color=TaxClassCode))+
   geom_line()

  multiplot(test1,test2,test3)

}
```
